### 2022-09-09 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_julia_for_ecologists@738048d03f64b40771406b32f43895c9d9a41177 🚀

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily Solving the \(n\)-language problem in ecology}
\vskip 5em

@@

@@

\textbf{Concept fig here}

>>>>

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily Solving the \(n\)-language problem: A
ecologist's guide to learning Julia}
\vskip 5em

@@

\begin{figure}
\centering
\includegraphics{./figures/multiple_dispatch.png}
\caption{TODO: caption. Adapted from Karpinski 2019 ``The unreasonable
effectiveness of multiple dispatch''}
\end{figure}

@@
